Name matching through deep learning

### 2018-11-19 old/paper2018/relatedWork.tex
words

\section{Related Work}
Extensions in data management systems for handling joins typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF; e.g., \cite{Cohen2003}.  String matching algorithms often do not work for merging different forms of the same entity because valid transformations of entity names can yield very different strings.  More recently, data driven approaches have emerged as a powerful alternative for merging data.  Data driven approaches mine patterns to determine the `rules' for joining a given entity type.  One example of such an approach is illustrated in \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.  Another example is work by \cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.  Our approach for merging datasets is much more general than either approach because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity, even if they cannot be directly expressed as program transforms.

The idea of building joint embeddings has been applied recently to the problem of linking relational tuples for entity resolution \cite{Mudgal},\cite{Bordawekar18}).  For the problem of linking tuples, each model that is learnt is specific to the database it was trained on because the attributes of an entity vary significantly across databases.  Our focus is on techniques for name matching, and we develop general purpose embedding models for merging alternate surface forms of key entities.

>>>>

\section{Related Work}
Extensions in data management systems for joins typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF; e.g., \cite{Cohen2003}.  String matching algorithms work poorly for merging the same entity because valid transformations of entity names can yield very different strings.  More recently, data driven approaches mine patterns to determine the `rules' for joining a given entity type.  One example is \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.  Another example is\cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.  Our approach for merging datasets is more general because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity, even if they cannot be directly expressed as program transforms.

Joint embeddings have been applied recently to linking relational tuples for entity resolution \cite{Mudgal},\cite{Bordawekar18}).  Here, each model is specific to the database on which it was trained because the attributes of an entity vary among databases.  Our focus is on techniques for name matching, and we develop general purpose embedding models for merging alternate surface forms of key entities.
